### 2023-12-04 main.tex
^-^

and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}^x$. {\color{blue} As a consequence, particles are injected and removed in the graph with different rates. When, for any $a\in \{1,\ldots,N\}$ there are at least two reservoirs at sites $x,y$ such that $\rho_{a}^{x}\neq  \rho_{a}^{y}$, a  non-zero current sets in, breaking the reversibility. Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.} %{\color{red}wants to fix}

@@

    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )_{x\in V}

@@

the extra-site $u(x)$ connected to $x\in V$. We state the following duality result.

@@

@@

\todo{what happens to $q_N$?} {\color{blue} we used the orthogonality between $\langle q_{1}^{u(x)} ,\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,q_{N}^{u(x)}\rangle=1$ on the extra-site $u(x)$}
where  we used the orthogonality relation \eqref{ortho}. 

@@

{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state distribution, i.e. it is given in \eqref{exactCorrelations}.}

@@

 We aim to compute the correlations between the sites $\mathbf{x}=\left(x_{1},\ldots,x_{m}\right)$ occupied by the species $\mathbf{a}=\left(a_{1},\ldots,a_{m}\right)$, such that $a_{1},\ldots,a_{m}\in \{2,\ldots,N\}$ i.e. 
\begin{equation}\label{Prob-m}
		\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{\text{stat}}&
		=\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)
where we denote $\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
This corresponds to the steady state probability of a chain of length $m$ with each coordinates $x_{i}$ occupied by $a_{i}\neq 1$.Therefore, using again the notation \eqref{notation} and calling $\tau_{i}=a_{i}$, we have 

>>>>

and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}^x$. {\color{blue} As a consequence, particles are injected and removed in the graph with different rates. When, for any $a\in \{1,\ldots,N\}$, there are at least two reservoirs at two different sites $x,y$ such that $\rho_{a}^{x}\neq  \rho_{a}^{y}$, a  non-zero current sets in, breaking the reversibility. Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.} %{\color{red}wants to fix}

@@

    \bm{\xi}=\left(\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )\right)_{x\in V}

@@

the extra-site $u(x)$ connected to $x\in V$. {\color{blue} We observe that the configuration variable at the extra site $u(x)$ does not have to satisfy any exclusion constraint, since it is defined on $\mathbb{N}_{0}^{N}$}. We state the following duality result.

@@

{\color{blue} Here $|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle$ is the vector associated to the configuration of in the extra site $u(x)$.  For all $q_{1},\ldots,q_{N}\in \mathbb{N}_{0}$, we assume that it satisfy an orthogonality relation
\begin{equation}\label{ortho-extraSite}
	\langle q_{1},\ldots,q_{N}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a}^{u(x)},q_{a}}
\end{equation} }

@@

\todo{what happens to $q_N$?} {\color{blue} 
where we used the orthogonality relation \eqref{ortho-extraSite}}. 

@@

{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state distribution, then it is given in \eqref{exactCorrelations}.}

@@

 We aim to compute the correlations between the sites% $\mathbf{x}=\left(x_{1},\ldots,x_{m}\right)$ occupied by the species $\mathbf{a}=\left(a_{1},\ldots,a_{m}\right)$, such that $a_{1},\ldots,a_{m}\in \{2,\ldots,N\}$ i.e. 
\begin{equation}%\label{Prob-m}
	%	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{\text{stat}}&
	%	=\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)
where we denote %$\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
This corresponds to the steady state probability of a chain of length %$m$ with each coordinates $x_{i}$ occupied by $a_{i}\neq 1$.Therefore, using again the notation \eqref{notation} and calling %$\tau_{i}=a_{i}$, we have 
